Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-09 bbbq_article.tex
Show pictures from SNPs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Subset of random sequences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../ncbi_peregrine/scripts/fig_f_snps_found_and_expected_per_n_tmhs.png}
  \caption{fig_f_snps_found_and_expected_per_n_tmhs}
  \label{fig:f_snps_found_and_expected_per_n_tmhs}
\end{figure}
)

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../ncbi_peregrine/scripts/fig_f_snps_found_and_expected.png}
  \caption{fig_f_snps_found_and_expected}
  \label{fig:f_snps_found_and_expected}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../ncbi_peregrine/scripts/fig_n_proteins_per_gene_name.png}
  \caption{fig_n_proteins_per_gene_name}
  \label{fig:n_proteins_per_gene_name}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../ncbi_peregrine/scripts/fig_n_snps_found_and_expected_per_n_tmhs.png}
  \caption{fig_n_snps_found_and_expected_per_n_tmhs}
  \label{fig:n_snps_found_and_expected_per_n_tmhs}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../ncbi_peregrine/scripts/fig_n_tmhs_per_protein.png}
  \caption{fig_n_tmhs_per_protein}
  \label{fig:n_tmhs_per_protein}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../ncbi_peregrine/scripts/fig_snp_rel_pos.png}
  \caption{fig_snp_rel_pos}
  \label{fig:snp_rel_pos}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../ncbi_peregrine/scripts/fig_snps_per_gene_name_ncbi.png}
  \caption{fig_snps_per_gene_name_ncbi}
  \label{fig:snps_per_gene_name_ncbi}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../ncbi_peregrine/scripts/fig_snps_per_gene_name.png}
  \caption{fig_snps_per_gene_name}
  \label{fig:snps_per_gene_name}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../ncbi_peregrine/scripts/fig_snps_per_gene_name_processed.png}
  \caption{fig_snps_per_gene_name_processed}
  \label{fig:snps_per_gene_name_processed}
\end{figure}
